The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-11 src/ms.tex
final paragraph on rates

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{commits_committers_per_month.pdf}
        \caption{
            \textbf{Top panel:} The number of Git commits per month (defined as
            consecutive 30 day windows) merged into to the \astropypkg core
            package over the whole history of the project (up to end of 2021,
            v5.0).
            The number clearly peaks just before feature freezes (vertical
            lines) as a flurry of activity leading up to each release, but in
            recent years the mean rate has remained steady at about $\sim$300
            commits per month.
            \textbf{Bottom panel:} The number of unique Git committers who
            contribute to the \astropypkg core package each month (again defined
            as consecutive 30 day windows).
            While this also shows some variation depending on proximity to
            feature freezes, in recent years the mean rate of unique
            contributors has remained consistent at about $\sim$22 committers
            per month.
        }
        \label{fig:contributor-summary:per-month}
    \end{centering}
\end{figure}

A final metric we consider ... rate of contributions and contributor participation ...

>>>>

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.75\textwidth]{commits_committers_per_month.pdf}
        \caption{
            \textbf{Top panel:} The number of Git commits per month (defined as
            consecutive 30 day windows) merged into to the \astropypkg core
            package over the whole history of the project (up to end of 2021,
            v5.0).
            The dark line shows the mean rate using a 1 year rolling window, but
            the under-plotted gray line shows the raw monthly rate.
            The raw number clearly peaks just before feature freezes (vertical
            lines) as a flurry of activity leading up to each release, but in
            recent years the mean rate has remained steady at about $\sim$300
            commits per month.
            \textbf{Bottom panel:} Similar to above, but now showing the number
            of unique Git committers who contribute to the \astropypkg core
            package each month (again defined as consecutive 30 day windows).
            While this also shows some variation depending on proximity to
            feature freezes, in recent years the mean rate of unique
            contributors has remained consistent at about $\sim$22 committers
            per month.
        }
        \label{fig:contributor-summary:per-month}
    \end{centering}
\end{figure}

A final metric we consider as a diagnostic of the contributor base and
contributions to the \astropypkg core package is the rate of contributions and
contributor participation, defined again using Git commits to quantify
contributions.
Figure~\ref{fig:contributor-summary:per-month} shows the monthly rates of
commits and unique committers to the \astropypkg core package over the history
of the package.
After an initial ramp-up in the commit rate and number of committers (lasting
roughly from 2011 to 2014), the commit rate and number of unique committers have
both remained fairly constant.
